Parallel for Oregon Zip and WRF_Grid Intersection Proportion

### 2017-04-25 r_scripts/parallel_presentation.Rmd

vars1 <- c(1:1610)
z <- rep(201:300, each=100)
w <- rep(201:300,100)
```

@@

```{r forloop}
start <- proc.time()
for (i in 201:300) {
  # output value of zipcode
  zipcode <- or_zip_name[i]
  # limit shapefile to particular zipcode
  zip_shape <- or_zip_map[or_zip_map$ZCTA5CE10 %in% zipcode, ]
  # convert to polygon
  zip_poly <-SpatialPolygons(zip_shape@polygons)
for(j in 201:300){
    # output each grid and create a polygon
    wrf_grid <- smoke_grid[smoke_grid@data$WRFGRID_ID == j, ]
    wrf_poly <- SpatialPolygons(wrf_grid@polygons)

>>>>

vars1 <- c(1:1610)
z <- rep(1:417, each=1610)
w <- rep(1:1610,417)
```

@@

```{r forloop}
start <- proc.time()
for (i in 1:417) {
  # output value of zipcode
  zipcode <- or_zip_name[i]
  # limit shapefile to particular zipcode
  zip_shape <- or_zip_map[or_zip_map$ZCTA5CE10 %in% zipcode, ]
  # convert to polygon
  zip_poly <-SpatialPolygons(zip_shape@polygons)
for(j in 1:1610){
    # output each grid and create a polygon
    wrf_grid <- smoke_grid[smoke_grid@data$WRFGRID_ID == j, ]
    wrf_poly <- SpatialPolygons(wrf_grid@polygons)
